---
title: "theCLE"
author: "Leilani Guerrero"
date: 'Summer 2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")

```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

 
Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

 It appears to me that the plot is not unimodal because it has 3 peaks but they are not the same size. The peak in the middle is the highest peak while the two next to it are the same size. The mean of the plot is 49.2 and the SD is 29.5

Do this again for 4 random samples
```{r}
numb = 4
Kdata <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

It appears to me that the plot is not unimodal because it has 3 peaks but they are not the same size. The peak in the middle is the highest peak while the two next to it are the same size, it also has two little humps in the begging and the end of the plot. The mean of the plot is 50.3 and the sd is 20.6

Then again for 9 random samples
```{r}
numb = 9
Kdata <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

It appears to me that the plot is not unimodal because it has 2 peaks but they are not the same size. The peak to the left is the lower peak while the one to the right is the higher one. there is also two little humps on the side of the 2 peaks. The mean of the plot is 50.4 and the sd is 13.6.

then 16 random samples
```{r}
numb = 16
Kdata <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```

It appears to me that the plot is not unimodal because it has 3 peaks but they are not the same size. The peak in the middle is the highest peak while the two next to it are the same size. 

finally for 36 random samples.
```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
```

It appears to me that the plot is not unimodal because it has 3 peaks but they are not the same size. The peak in the middle is the highest peak while the two next to it are the same size. 

Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.